An Efficient Minibatch Acceptance Test for MCMC

### 2016-06-21 nips_2016.tex
updated MH_test

\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\begin{algorithm}[t]
\Input{Number of samples $T$, minibatch size $m$, pre-computed $X_{\rm
corr}$ distribution, and initial sample $\theta_0$.}
\Output{A chain of $T$ samples $\{\theta_1, \ldots, \theta_T\}$ for either posterior inference or
MAP/ML estimation.}
\For{$t=\{1, \ldots, T\}$}{
    Propose a candidate $\theta'$\ from proposal distribution\;
    Draw a minibatch of $m$ samples, compute $\Delta'(\theta',\theta_t)$ and ${\rm std}(\Delta')$ for this sample\;
    \While {${\rm std}(\Delta') \ge 1.2$} {
    	Draw $m$ more samples to augment the current minibatch, and update $\Delta'$ and ${\rm std}(\Delta')$ \;
    }
    Let $\sigma = \sqrt{1.2 - {\rm std}(\Delta')^2}$, draw a normal variable $X_n \in Norm(0,\sigma)$ and
    $X_c$ from the correction distribution\;

>>>>

\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\begin{algorithm}[t]
\Input{Number of samples $T$, minibatch size $m$, pre-computed $X_{\rm
corr}$ distribution, and initial sample $\theta_0$.}
\Output{A chain of $T$ samples $\{\theta_1, \ldots, \theta_T\}$ from $p(\theta)$\;
MAP/ML estimation.}
\For{$t=\{1, \ldots, T\}$}{
    Propose a candidate $\theta'$\ from proposal distribution\;
    Draw a minibatch of $m$ samples, compute $\Delta'(\theta',\theta_t)$ and ${\rm std}(\Delta')$ for this sample\;
    \While {${\rm std}(\Delta') \ge 1$} {
    	Draw $m$ more samples to augment the current minibatch, and update $\Delta'$ and ${\rm std}(\Delta')$ \;
    }
    Let $\sigma = \sqrt{1 - {\rm std}(\Delta')^2}$, draw a normal variable $X_n \in Norm(0,\sigma)$ and
    $X_c$ from the correction distribution\;
